data_collation

### 2024-05-03 scripts/data_collation.Rmd
updated metadata sheet

# Convert species names to codes
for (col in names(swath)) {
  swath[, col] <- species.metadata$code[match(swath[, col], species.metadata$species.substrate)]
}

>>>>

# Convert species names to codes
updated.swath <- for (col in names(swath)) {
  swath[, col] <- species.metadata$code[match(swath[, col], species.metadata$species.substrate)]
}
